Covariate analysis of CMC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (ACC and DLPFC with CQN normlaisation)

### 2017-05-19 code/Rmd/CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN.Rmd
Major modifications to account for new model selection with SVA

## Explore metatdata
```{r data.explore, fig.width = 12, fig.height = 12}
my.theme <- theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1), plot.title=element_text(hjust=0.5))

>>>>

### Explore metatdata
```{r data.explore, fig.width = 12, fig.height = 12}
my.theme <- theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1), plot.title=element_text(hjust=0.5))
